Missing The Point

### 2020-09-17 Manuscript.Rmd
Run sim with different CI computation to check why coverages are so off (n_sim = 100, maxit = 5)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r echo=FALSE}
load("~/MissingThePoint/Data/results.Rdata")
results %>%
  ggplot() +
  geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results.Rdata")

@@

```{r echo=FALSE}
results %>%
  ggplot() +
  geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

Update with different CI computation, see https://stefvanbuuren.name/fimd/sec-evaluation.html#sec:quantifyingbias

@@

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.mu.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.mu.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.mu.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.mu.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()

```
```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.sigma.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.sigma.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.sigma.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.sigma.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.qhat, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.qhat, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.qhat, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.qhat, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

## Discussion

- Estimates etc do not improve after it = 7

- Convergence diagnostics keep improving, but are all stable after 20-30 it

- Univariate thetas do not differentiate between missingness mechanisms or proportions of incomplete cases

- Determining non-stationarity with lambda is more difficult than with qhat :(
